Cognitive and Auditory Predictors of Dysarthric Speech Understanding in Older

### 2024-01-10 Manuscript Analyses/manuscript_analysis.Rmd
Added best_win to intel change models

@@

The important variables for the PDM10 models is shown below. The interaction between working memory and words in noise hearing threshold is the most important predictor, followed by the main effect of words in noise hearing threshold, the interaction between working memory and receptive vocabulary, the interaction between cognitive flexibility and processing speed, the interaction between inhibiotry control and words in noise hearing threshold, the interaction between receptive vocabulary and processing speed, and the interaction between working memory and cognitive flexibility.

@@

@@

The relative importance of the model variables are shown in the figure below.

@@

mod_fun2 <- function(speaker, title) {
  subsetted = cor_df %>%
    dplyr::select(-c(fluid_cog_c, pic_seq_c, improvement)) %>%
    dplyr::mutate(pwc_diff = resid(lm(posttest ~ pretest))) %>%
    dplyr::select(pwc_diff, ends_with("_c"), speaker) %>%
    tidyr::drop_na(pwc_diff, ends_with("_c"), speaker) %>%
    dplyr::filter(speaker == {{speaker}}) %>%
    dplyr::select(-speaker) %>%
    rename(pwc = pwc_diff)

@@

effect_plot(mods12, list_sort_c, vocab_c) # Working Memory * Receptive Vocabulary
effect_plot(mods12, vocab_c, list_sort_c) # Receptive Vocabulary * Working Memory
effect_plot(mods12, list_sort_c, int = F) # Working Memory
effect_plot(mods12, pattern_c, int = F) # Processing Speed
effect_plot(mods12, list_sort_c, flanker_c) # Working Memory * Inhibitory Control
effect_plot(mods12, flanker_c, list_sort_c) # Inhibitory Control * Working Memory

@@

The relative importance of the model variables is shown in the figure below.

@@

effect_plot(mods22, vocab_c, int = F) # Receptive Vocab 
effect_plot(mods22, flanker_c, int = F) # Inhibitory Control
effect_plot(mods22, card_sort_c, vocab_c) # Cognitive Flexibility * Receptive Vocab

>>>>

# Removing Participant 323 from the dataset (missing demographic and cognitive data)

data <- data %>%
  dplyr::filter(id != 323)

demo <- demo %>%
  dplyr::filter(id != 323)

@@

The important variables for the PDM10 models is shown below. The interaction between working memory and words in noise hearing threshold is the most important predictor, followed by the main effect of words in noise hearing threshold, the interaction between working memory and receptive vocabulary, the interaction between cognitive flexibility and processing speed, the interaction between inhibitory control and words in noise hearing threshold, the interaction between receptive vocabulary and processing speed, and the interaction between working memory and cognitive flexibility.

@@

Plotting the interaction effects for the PDM10 initial intelligibility models.

@@

The relative importance of the model variables are shown in the figure below. The most important variable in the model is the interaction between inhibitory control and words in noise hearing threshold followed by the interaction between processing speed and words in noise threshold, the interaction between cognitive flexibility and words in noise hearing threshold, and the interaction between inhibitory control and receptive vocabulary.

@@

mod_fun2 <- function(speaker, title) {
  subsetted = cor_df %>%
    dplyr::select(-c(fluid_cog_c, pic_seq_c, improvement)) %>%
    dplyr::mutate(pwc_diff = resid(lm(posttest ~ pretest))) %>%
    dplyr::select(pwc_diff, ends_with("_c"), speaker, best_win) %>%
    tidyr::drop_na(pwc_diff, ends_with("_c"), speaker, best_win) %>%
    dplyr::filter(speaker == {{speaker}}) %>%
    dplyr::select(-speaker) %>%
    rename(pwc = pwc_diff)

@@

effect_plot(mods12, flanker_c, best_win) # Inhibitory Control * Words in Noise Threshold
effect_plot(mods12, pattern_c, best_win) # Processing Speed * Words in Noise Threshold
effect_plot(mods12, card_sort_c, best_win) # Cognitive Flexibility * Words in Noise Threshold
effect_plot(mods12, flanker_c, vocab_c) # Inhibitory Control * Receptive Vocabulary
effect_plot(mods12, vocab_c, flanker_c) # Receptive Vocabulary * Inhibitory Control

@@

The relative importance of the model variables is shown in the figure below. The most important variable in the model is the interaction between cognitive flexibility and receptive vocabulary followed by the interaction between inhibitory control and processing speed, the main effect of receptive vocabulary, the main effect of inhibitory control, and the interaction between inhibitory control and words in noise hearing threshold.

@@

effect_plot(mods22, card_sort_c, vocab_c) # Cognitive Flexibility * Receptive Vocabulary
effect_plot(mods22, vocab_c, card_sort_c) # Receptive Vocabulary * Cognitive Flexibility
effect_plot(mods22, flanker_c, pattern_c) # Inhibitory Control * Processing Speed
effect_plot(mods22, pattern_c, flanker_c) # Processing Speed * Inhibitory Control
effect_plot(mods22, vocab_c, int = F) # Receptive Vocab 
effect_plot(mods22, flanker_c, int = F) # Inhibitory Control
effect_plot(mods22, flanker_c, best_win) # Inhibitory Control * Words in Noise Threshold
effect_plot(mods22, best_win, flanker_c) # Words in Noise Threshold * Inhibitory Control
